---
title: "Are K-Pop idols debuting too young nowadays?"
author: "Flavia Jiang"
date: "2023-03-02"
output: 
  pdf_document: 
    latex_engine: xelatex
---

Note: Not all graphs created in this file were presented in the article. For some reasons, Chinese characters failed to display in the code chunks when knitted to pdf. However, they still appeared in the graphs.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(ggplot2)
library(showtext)
library(tidyr)
library(ggrepel)
showtext_auto()
```

# Default styles for ggplot2

```{r}
style <- theme_light() +
  theme(
    axis.title = element_text(color = "#737373", size = 11),
    axis.text = element_text(size = 9, color = "#737373"),
    legend.title = element_text(color = "#737373", size = 11),
    legend.text = element_text(color = "#737373", size = 9),
    plot.title = element_text(
      color = "#737373",
      size = 15,
      margin = margin(10, 0, 10, 0)
    ),
    axis.title.x = element_text(margin = margin(
      t = 7,
      r = 0,
      b = 7,
      l = 0
    )),
    axis.title.y = element_text(margin = margin(
      t = 0,
      r = 7,
      b = 0,
      l = 7
    )),
    plot.caption = element_text(color = "#737373", size = 9)
  )
```

# Data cleaning

## Data by idol

```{r}
dat <- read.csv("debut_age.csv")
# The memberdat dataframe: one idol per row
memberdat <- pivot_longer(dat,
                          cols = 6:28,
                          names_to = "member",
                          values_to = 'age')
memberdat <- filter(memberdat,!is.na(age))
head(memberdat)
```

## Data by group

Variables:

-   average: average debut age of the group
-   numMember: number of members
-   ageSum: sum of debut ages of the members 
-   sd: standard deviation of debut ages 
-   adult: number of members aged 18 or above when debutting / numMember

```{r}
# The groupdat dataframe: one group per row
groupdat <-
  summarise(
    group_by(memberdat, group),
    average = mean(age),
    numMember = n(),
    ageSum = sum(age),
    sd = sd(age),
    company = unique(company)[1],
    gender = unique(gender)[1],
    show = unique(show)[1],
    adult = sum(age >= 18) / n(),
    debut_year = unique(debut_year)[1]
  )
head(groupdat)
```

# Basic statistics (overall)

## Distribution of debut age

```{r}
median(memberdat$age)
mean(memberdat$age)
ggplot(data = memberdat, aes(x = age)) + geom_histogram(breaks = 14:29) + style
```

## Distribution of debut age by debut year

```{r}
year_mean <-
  summarize(group_by(memberdat, debut_year),
            average = mean(age),
            count = n())[4:21, ]
year_median <-
  summarize(group_by(memberdat, debut_year),
            median = median(age),
            count = n())[4:21, ]

ggplot(data = memberdat, aes(x = debut_year, y = age)) +
  geom_jitter(width = 0.02, height = 0.3) +
  style

sum_member <-
  summarize(group_by(memberdat, debut_year, age), count = n())
ggplot() +
  geom_point(
    data = sum_member,
    aes(x = debut_year, y = age, size = count),
    color = "#a78bfa",
    alpha = 0.5
  ) +
  style +
  geom_hline(
    yintercept = c(19, 18.89),
    linetype = "dashed",
    size  = 0.5,
    color = c("#fb7185", "#38bdf8"),
    alpha = 0.5
  ) +
  geom_path(
    data = year_median,
    color = "#fb7185",
    alpha = 0.6,
    size = 1,
    aes(x = debut_year, y = median)
  )  + labs(x = "出道年份",
            y = "出道年龄",
            size = "出道人数",
            title = "出道年龄分布基本情况（以艺人为单位）") +
  geom_path(
    data = year_mean,
    color = "#38bdf8",
    alpha = 0.6,
    size = 1,
    aes(x = debut_year, y = average)
  ) +
  geom_label(aes(x = 2001.5, y = 19.8, label = "中位数: 19"),
             color = "#fb7185",
             size = 3.5) +
  geom_label(
    aes(x = 2001.5, y = 18.1, label = "平均数: 18.89"),
    color = "#38bdf8",
    size = 3.5
  ) +
  geom_label(aes(x  = 2005.2, y = 29, label = "最大出道年龄: 29"),
             color = "#a78bfa",
             size = 3.5) +
  geom_label(aes(x = 2012.2, y = 14, label = "最小出道年龄: 14"),
             color = "#a78bfa",
             size = 3.5) +
  scale_y_continuous(breaks = seq(from = 14, to = 28, by = 2)) +
  scale_x_continuous(breaks = seq(from = 1996, to = 2022, by = 2))

ggsave("debut_age_distribution.png",
       plot = last_plot(),
       device = png)

ggplot(data = year_mean) +
  geom_path(
    color = "#c4b5fd",
    arrow = arrow(),
    size = 1.5,
    aes(x = debut_year, y = average)
  ) +
  geom_point(
    aes(x = debut_year, y = average, size = count),
    color = "#a78bfa",
    alpha = .8
  )  +
  style

ggplot(data = year_median) +
  geom_path(
    color = "#c4b5fd",
    arrow = arrow(),
    size = 1.5,
    aes(x = debut_year, y = median)
  ) +
  geom_point(
    aes(x = debut_year, y = median, size = count),
    color = "#a78bfa",
    alpha = .8
  )  +
  style
```

## Distribution of group average debut ages

```{r}
ggplot(data = groupdat, aes(x = average)) +
  geom_histogram(fill = "#ddd6fe") +
  style

head(groupdat[order(groupdat$average), ])
```

```{r, fig.height = 4.5, width = 6}
ggplot(data = groupdat, aes(x = debut_year, y = average)) +
  geom_point(color = "#8b5cf6") +
  geom_label(
    label = groupdat$group,
    nudge_x = 0.1,
    nudge_y = 0.1,
    size = 2.5,
    color = "#8b5cf6"
  ) +
  labs(
    x = "出道年份",
    y = "平均出道年龄",
    title = "出道年龄分布情况（以团体为单位）",
    caption = "注: NCT的分队NCT DREAM平均出道年龄为15.6。此处只显示大队数据。\n注: 长方形部分可见下方放大图。"
  ) +
  style +
  scale_y_continuous(breaks = 16:22) +
  scale_x_continuous(breaks = seq(from = 1996, to = 2022, by = 2)
  ) +
  geom_rect(
    aes(
      xmin = 2014,
      xmax = 2020,
      ymin = 18,
      ymax = 20
    ),
    fill = NA,
    color = "#a3a3a3",
    linetype = "dashed"
  ) +
  geom_label(aes(x = 2001.5, y = 19.2, label = "中位数: 19"),
             color = "#fb7185",
             size = 2.5) +
  geom_label(
    aes(x = 2001.5, y = 18.6, label = "平均数: 18.81"),
    color = "#38bdf8",
    size = 2.5
  ) +
  geom_hline(
    yintercept = c(19, 18.81),
    linetype = "dashed",
    size = 0.5,
    color = c("#fb7185", "#38bdf8"),
    alpha = 0.6
  )

ggsave("group_mean_debut_age.png",
       plot = last_plot(),
       device = png)

ggplot(data = groupdat, aes(x = debut_year, y = average)) +
  geom_point(color = "#8b5cf6") +
  geom_label_repel(
    label = groupdat$group,
    size = 3,
    color = "#8b5cf6",
    fill = NA,
    max.overlaps = 20,
    min.segment.length = 1
  ) +
  ylim(c(18, 20)) + xlim(c(2014, 2020)) +
  style +
  labs(x = "出道年份", y = "平均出道年龄", title = "出道年龄分布情况（以团体为单位）") +
  geom_hline(
    yintercept = c(19, 18.81),
    linetype = "dashed",
    size = 0.5,
    color = c("#fb7185", "#38bdf8"),
    alpha = 0.6
  ) +
  geom_label(aes(x = 2019, y = 19, label = "中位数: 19"),
             color = "#fb7185",
             size = 3) +
  geom_label(aes(x = 2019, y = 18.8, label = "平均数: 18.81"),
             color = "#38bdf8",
             size = 3)

ggsave("group_mean_debut_age_zoomed_in.png",
       plot = last_plot(),
       device = png)
```

## Distribution of debut age standard deviations within groups

```{r}
ggplot(data = groupdat, aes(x = sd)) +
  geom_histogram(fill = "#ddd6fe") +
  labs(x = "各团出道年龄方差",  y = "频率") +
  theme_light() +
  theme(axis.title = element_text(colour = "#4b5563", size = 12),
        axis.text = element_text(size = 11))

filter(groupdat, sd > 3) # 2NE1, After School, Le Sserafim, WannaOne, X1, Kepler
filter(groupdat, sd < 0.7)
```

```{r, fig.height = 4, width = 6}
ggplot(data = groupdat, aes(x = debut_year, y = sd)) +
  geom_point(color = "#8b5cf6") +
  geom_label(
    label = groupdat$group,
    nudge_x = 0.2,
    nudge_y = 0.1,
    size = 2.5,
    color = "#8b5cf6",
  ) + theme_light()

summarize(group_by(memberdat, group), diff = max(age) - min(age))
```

## Distribution of adult rates

```{r}
ggplot(data = groupdat, aes(x = adult)) + 
  geom_histogram( fill = "#ddd6fe") +
  labs( x = "各团出道成年比例",  y = "频率", caption = "注：18岁为成年。", title = "各团出道成年比例分布") +
  theme_light() + 
  style +
  geom_vline(xintercept = 0.75, linetype = "dashed", size = 1, color = c("#fb7185"), alpha = 0.6)+
  geom_label(aes(x = 0.75, y = 10, label = "中位数: 0.75"), color= "#fb7185", size  = 4) 

ggsave(
  "adult_percentage.png",
  plot = last_plot(),
  device = png)

filter( groupdat, adult == 1) 
filter( groupdat, adult == 0) # Only one: S.E.S.
median( groupdat$adult)
```

# Analysis by gender

```{r}
ggplot() +
  geom_histogram(
    data = memberdat,
    aes(x = age, fill = gender),
    position = "identity",
    alpha = 0.5,
    breaks = 14:29
  ) +
  style +
  labs(x = "出道年龄",
       y = "频率",
       fill = "性别",
       title = "出道年龄分布与性别（以个人为单位）") +
  geom_label(
    aes(x = 25.5, y  = 42, label = "男爱豆平均出道年龄: 19.1"),
    color = "#38bdf8",
    size  = 4
  ) +
  geom_label(
    aes(x = 25.5, y = 37, label = "女爱豆平均出道年龄: 18.6"),
    color = "#fb7185",
    size  = 4
  ) +
  scale_fill_manual(values = c("#fb7185", "#38bdf8"))

ggsave("debut_age_by_gender_bar.png",
       plot = last_plot(),
       device = png)

mean(filter(memberdat, gender == "F")$age)
median(filter(memberdat, gender == "F")$age)
mean(filter(memberdat, gender == "M")$age)
median(filter(memberdat, gender == "M")$age)

t.test(
  filter(memberdat, gender == "F")$age,
  filter(memberdat, gender == "M")$age,
  alternative = "less"
)

```

## Average debut age

```{r pressure, echo=TRUE}
dat_f <- filter(groupdat, gender == "F")
sum(dat_f$ageSum) / sum(dat_f$numMember) # 18.6
median(dat_f$average) # 19

dat_m <- filter(groupdat, gender == "M")
sum(dat_m$ageSum) / sum(dat_m$numMember) # 19
median(dat_m$average) # 19

ggplot(data = groupdat, aes(x = debut_year, y = average, color = gender)) +
  geom_point(alpha = 0.7) +
  style +
  labs(
    caption = "注: NCT的小分队NCT DREAM出道平均年龄为15.6岁。图上只显示NCT全体的平均年龄。",
    title = "各团平均出道年龄与性别（以团体为单位）",
    x = "出道年份",
    y = "平均出道年龄",
    color = "性别"
  ) +
  scale_color_manual(values = c("#fb7185", "#38bdf8"))

ggsave("debut_age_by_gender_scatterplot.png",
       plot = last_plot(),
       device = png)

ggplot(data = memberdat, aes(x = debut_year, y = age, color = gender)) +
  geom_jitter(alpha = 0.7) +
  style +
  labs(
    caption = "注: NCT的小分队NCT DREAM出道平均年龄为15.6岁。图上只显示NCT全体的平均年龄。",
    title = "各团平均出道年龄与性别（以个人为单位）",
    x = "出道年份",
    y = "平均出道年龄",
    color = "性别"
  ) +
  scale_color_manual(values = c("#fb7185", "#38bdf8"))

ggplot(data = groupdat, aes(x = debut_year, y = average, color = gender)) + geom_point() +
  geom_label(
    label = groupdat$group,
    nudge_x = 0.2,
    nudge_y = 0.1,
    size = 2.5
  ) + style

ggplot(data = groupdat, aes(x = average, fill = gender)) + geom_histogram(alpha = 0.5, position = "identity")

t.test(dat_f$average, dat_m$average, alternative = "less")
# one-tail test: p-value < 0.1 -> different means

filter(memberdat, gender == "F", age <= 14)
filter(memberdat, gender == "M", age <= 14)
```

-   Median is the same. The difference between means is statistically significant.

## SD of debut ages within groups

```{r}
median(dat_m$sd)
median(dat_f$sd)

ggplot(data = groupdat, aes(x = sd, fill = gender))+ 
  geom_histogram(alpha = 0.5, position = "identity")+
  style +
  scale_fill_manual( values = c("#fb7185", "#38bdf8")) +
  labs(title = "团内年龄标准方差与性别", x = "年龄标准方差", y = "频率", fill = "性别")

ggsave(
  "stddev_by_gender.png",
  plot = last_plot(),
  device = png)

t.test(dat_m$sd, dat_f$sd, alternative = "less")
```

## Adult rate

```{r}
ggplot(data = groupdat, aes(x = adult , fill = gender)) +
  geom_histogram(alpha = 0.5, position = "identity")
t.test(dat_f$adult, dat_m$adult, alternative = "less")
```

# Analysis by company

## Average debut age

```{r, fig.height = 4}
ggplot(data = groupdat, aes(x = debut_year, y = average, color = company)) + geom_point() +
  geom_label(
    label = groupdat$company,
    nudge_x = 0.2,
    nudge_y = 0.1,
    label.size = 0.4,
    size = 2.5
  ) + style +
  labs(
    title = "各团出道平均年龄与所属公司",
    x = "出道年份",
    y = "出道平均年龄",
    color = "所属公司",
    caption = "注: 被HYBE收购的公司历代的团体都算在HYBE。"
  )

ggsave("group_mean_debut_age_by_company.png",
       plot = last_plot(),
       device = png)

summarize(group_by(memberdat, company), avg = mean(age))
```

## Adult rate

```{r, fig.height = 4}
ggplot(data = groupdat, aes(x = debut_year, y = adult, color = company)) + geom_point() +
  geom_label(
    label = groupdat$company,
    nudge_x = 0.2,
    nudge_y = 0.02,
    size = 2.5
  ) + style

summarize(group_by(groupdat, company),
          total = sum(numMember * adult) / sum(numMember))
```

# Talent show or not

## Average debut age

```{r}
dat_y <- filter(groupdat, show == "Y")
dat_n <- filter(groupdat, show == "N")
median(dat_y$average)
median(dat_n$average)

mean(dat_y$average)
mean(dat_n$average)

t.test(dat_y$average, dat_m$average, alternative = "less") # p-value is 0.12.

ggplot(data = groupdat, aes(x = debut_year, y = average, color = show)) + geom_point() + style
```

## SD

```{r}
ggplot(data = groupdat, aes(x = debut_year, y = sd, color = show)) + geom_point() + style
```

## Adult rate

```{r}
ggplot(data = groupdat, aes(x = debut_year, y = adult, color = show)) + geom_point() + style
```

# Analysis by generation

-   1st gen: - 2005
-   2nd gen: 2005 - 2009
-   3rd gen: 2010 - 2014
-   4th gen: 2015 - 2018
-   5th gen: 2019 - present

```{r}
groupdat$gen <- NA
groupdat[groupdat$debut_year < 2005, ]$gen <- 1
groupdat[groupdat$debut_year < 2010 & groupdat$debut_year > 2004, ]$gen <- 2
groupdat[groupdat$debut_year < 2015 & groupdat$debut_year > 2009, ]$gen <- 3
groupdat[groupdat$debut_year < 2019 & groupdat$debut_year > 2014, ]$gen <- 4
groupdat[groupdat$debut_year > 2018, ]$gen <- 5

memberdat$gen <- NA
memberdat[memberdat$debut_year < 2005, ]$gen <- 1
memberdat[memberdat$debut_year < 2010 & memberdat$debut_year > 2004, ]$gen <- 2
memberdat[memberdat$debut_year < 2015 & memberdat$debut_year > 2009, ]$gen <- 3
memberdat[memberdat$debut_year < 2019 & memberdat$debut_year > 2014, ]$gen <- 4
memberdat[memberdat$debut_year > 2018, ]$gen <- 5
```

## Average debut age

```{r}
summarize(group_by(memberdat, gen), median = median(age))
summarize(group_by(memberdat, gen), average = mean(age))

ggplot(data = groupdat, aes(x = debut_year, y = average, color = factor(gen))) +
  geom_point(alpha = 1, size = 1.5) + style +
  scale_x_continuous(breaks = c(1995, 2005, 2010, 2015, 2019)) +
  labs(
    title = "各团平均出道年龄与年代",
    y = "平均出道年龄",
    x = "出道年份",
    color = "出道年代",
    caption = "注: 2代与4代平均出道年龄线重合。"
  )  +
  scale_color_manual(
    values = c("#fb923c", "#facc15", "#a3e635", "#22d3ee", "#a78bfa"),
    labels = c("1代", "2代", "3代", "4代", "5代")
  )  +
  geom_hline(
    yintercept = c(17.64, 18.93, 19.36, 18.94, 18.45),
    linetype = "dashed",
    size = 0.5,
    color = c("#fb923c", "#facc15", "#a3e635", "#22d3ee", "#a78bfa")
  )

ggsave(
  "group_mean_debut_age_by_generation.png",
  plot = last_plot(),
  device = png)

four <- filter(memberdat, gen == 4)
five <- filter(memberdat, gen == 5)
t.test(four$age, five$age, alternative = "greater")
```

## Adult rate

```{r}
summarize(group_by(groupdat, gen),
          adult = sum(numMember * adult) / sum(numMember))
ggplot(data = groupdat, aes(x = debut_year, y = adult, color = factor(gen))) + geom_point() + style
```

# Analysis by company and gender

```{r}
sum_avg <- summarize(group_by(groupdat, company, gender), average = sum(ageSum)/sum(numMember))
sum_avg
summarize(group_by(groupdat, company, gender),  median = median(average))

sum_adult <- summarize(group_by(groupdat, company, gender),adult=sum(numMember*adult)/sum(numMember))
```

1.  average by company by gender

-   CUBE: male(20.3) - female(18.2) = 2.1
-   HYBE: male(18.1) - female(19.2) = -1.1
-   JYP: male(19.2) - female(17.8) = 1.4
-   OTHER: 0.5

2.  median

-   CUBE: male(22.2) - female(17.9) = 2.3

3.  adult%

-   CUBE: male(0.94) - female(0.65) = 0.29!!!
-   HYBE: female \> male
-   JYP: male(0.85) - female(0.66) = 0.19
-   OTHER: female \< male

```{r}
ggplot(data = sum_avg, aes(x = company, y = average - 14, fill = gender)) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           width = 0.8) +
  scale_fill_manual(values = c('#fecdd3', '#bae6fd')) + style +
  geom_text(
    aes(label = format(round(average, 2), nsmall = 2)),
    vjust = 1.6,
    color = "#6b7280",
    position = position_dodge(0.9),
    size = 3,
    fontface = "bold"
  ) +
  labs(title = "艺人平均出道年龄与公司+性别",
       x = "所属公司",
       y = "平均出道年龄",
       fill = "性别") +
  scale_y_continuous(labels = c("14", "16", "18", "20"),
                     breaks = c(0, 2, 4, 6))

ggsave(
  "mean_debut_age_by_company_and_gender.png",
  plot = last_plot(),
  device = png)
```

```{r}
ggplot(data=sum_adult, aes(x = company, y = adult, fill=gender)) +
geom_bar(stat="identity", position=position_dodge()) +
scale_fill_manual(values=c('#fecdd3','#bae6fd')) + style +
    geom_text(aes(label= format(round(adult,2), nsmall = 2)), vjust=1.6, color="#6b7280",
            position = position_dodge(0.9), size=3.5, fontface = "bold") +
  labs(title = "艺人出道成年率与公司+性别", x = "所属公司", y = "出道成年率", fill = "性别")

ggsave(
  "adult_percentage_by_company_and_gender.png",
  plot = last_plot(),
  device = png)
```

# Analysis by gender and generation

```{r}
sum_avg <- summarize(group_by(memberdat, gen, gender), average = mean(age), count = n())
sum_adult <- summarize(group_by(groupdat, gen, gender),  adult = sum(numMember*adult) / sum(numMember))
sum_avg
sum_adult
```

```{r}
ggplot(data = sum_avg) + geom_path(aes(x = gen, y = average, color = gender),
                                   size = 1.5,
                                   arrow = arrow()) + geom_point(aes(
                                     x = gen,
                                     y = average,
                                     color = gender,
                                     size = count
                                   )) + style +
  scale_color_manual(values = c('#fecdd3', '#bae6fd')) +
  labs(
    title = "艺人平均出道年龄与年代+性别",
    x = "出道年代",
    y = "平均出道年龄",
    color = "性别",
    size = "出道人数"
  )

ggsave(
  "mean_debut_age_by_generation_and_gender.png",
  plot = last_plot(),
  device = png)

mean(filter(memberdat,gender=="F",gen==4)$age) - mean(filter(memberdat,gender=="M",gen==4)$age)
```
